Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-22 paper/ms.tex
summary paragraph in comparison section

@@

Many other approximate methods for scaling GP inference exist \citep[see, for
example,][and references therein]{Wilson:2015a} and we make no attempt to
discuss the comparisons exhaustively.

\dfmtodo{One more sentence in conclusion.}

>>>>

In practice, it is worth treating terms with $b_j=0$ and $d_j=0$ as a special
case because, for this term $j$, $\psi_{n,\,j}$, $h_{n,\,j}$, and $v_{n,\,j}$
will also be identically zero for all $n$.
Removing these trivial rows from the extended matrix results in factor of two
increase in the computational efficiency for these terms.
In our implementation, we refer to ``real'' terms as those where $b_j=0$ and
$d_j=0$, and the general terms are called ``complex''.

@@

Many other approximate methods for scaling GP inference exist \citep[see, for
example,][and references therein]{Wilson:2015a} and we make no attempt to make
our discussion exhaustive.
The key take away here is that \celerite\ provides and \emph{exact} method for
GP inference for a specific but flexible class of one-dimensional kernel
functions.
The closest cousin is the CARMA method with similar strengths and limitations
but, since there is a simpler relationship between the parameters of a
\celerite\ model and its behavior, \celerite\ can be more easily integrated
with physical or physically interpretable models.
